The \proglang{R} Package \pkg{forestinventory}: Design-Based Global and Small Area Estimations for Multi-Phase Forest Inventories

### 2017-09-18 JStatSoft_forestinventory_master-concordance.tex
update Andreas 18.09.2017(2)

\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:%
1 105 1 1 4 1 1 1 4 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Introduction.Rnw:ofs 113:%
1 97 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 211:%
121 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Main structure and modules of the Package.Rnw:ofs 221:%
1 131 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 353:%
132 11 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Twophase_Estimators and their Application.Rnw:ofs 365:%
1 189 1 1 2 4 0 1 2 14 1 1 5 7 0 1 2 2 1 1 2 24 0 1 2 4 1 1 2 4 0 1 2 2 1 1 2 1 0 1 5 6 0 1 2 3 1 1 2 8 0 1 2 157 1 1 7 6 0 1 1 26 0 1 2 3 1 1 2 13 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 5 1 1 6 5 0 1 1 8 0 1 2 7 1 1 2 4 0 1 2 1 1 1 6 5 0 1 1 3 0 1 2 1 1 1 2 11 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 959:%
145}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Threephase_Estimators and their Application.Rnw:ofs 960:%
1 119 1 1 2 8 0 1 2 4 1 1 2 1 0 1 1 3 0 1 2 4 1 1 4 1 1 1 6 8 0 1 2 2 1 1 2 27 0 1 2 4 1 1 4 6 0 1 2 2 1 1 2 8 0 1 2 193 1 1 3 2 0 1 1 3 0 1 2 4 1 1 8 11 0 1 3 1 1 1 4 1 1 1 2 12 0 1 2 4 1 1 7 9 0 1 2 2 1 1 2 12 0 1 2 7 1 1 7 10 0 1 3 2 1 1 2 12 0 1 2 6 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1479:%
147 11 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Calculation of Confidence Intervals.Rnw:ofs 1491:%
1 42 1 1 2 11 0 1 2 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1556:%
160 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Special Cases and Scenarios.Rnw:ofs 1566:%
1 20 1 1 2 4 0 1 2 4 1 1 6 8 0 1 2 4 1 1 6 8 0 1 2 18 1 1 8 16 1 1 7 9 0 1 2 2 1 1 2 8 0 1 2 2 1 1 2 8 0 1 2 4 1 1 2 8 0 1 2 22 1 1 3 5 0 1 2 27 1 1 3 5 0 1 2 39 1 1 3 5 0 1 2 23 1 1 3 5 0 1 2 19 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1863:%
171 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Analysis and Visualization.Rnw:ofs 1873:%
1 20 1 1 4 6 0 1 2 3 1 1 6 8 0 1 2 2 1 1 7 9 0 1 2 2 1 1 7 9 0 1 2 2 1 1 8 10 0 1 2 4 1 1 5 7 0 1 2 6 1 1 2 4 0 1 2 2 1 1 2 26 0 1 2 16 1 1 4 1 1 1 2 11 0 1 2 18 1 1 5 7 0 1 2 4 1 1 3 5 0 1 2 10 1 1 2 4 0 1 2 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 2104:%
182 8 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Acknowledgements.Rnw:ofs 2113:%
1 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 2118:%
192 11 1}

>>>>

\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:%
1 107 1 1 4 1 1 1 4 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Introduction.Rnw:ofs 115:%
1 97 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 213:%
123 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Main structure and modules of the Package.Rnw:ofs 223:%
1 131 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 355:%
134 11 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Twophase_Estimators and their Application.Rnw:ofs 367:%
1 203 1 1 2 4 0 1 2 14 1 1 5 7 0 1 2 2 1 1 2 24 0 1 2 4 1 1 2 4 0 1 2 2 1 1 2 1 0 1 5 6 0 1 2 3 1 1 2 8 0 1 2 157 1 1 7 6 0 1 1 26 0 1 2 3 1 1 2 13 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 5 1 1 6 5 0 1 1 8 0 1 2 7 1 1 2 4 0 1 2 1 1 1 6 5 0 1 1 3 0 1 2 1 1 1 2 11 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 975:%
147}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Threephase_Estimators and their Application.Rnw:ofs 976:%
1 119 1 1 2 8 0 1 2 4 1 1 2 1 0 1 1 3 0 1 2 4 1 1 4 1 1 1 6 8 0 1 2 2 1 1 2 27 0 1 2 4 1 1 4 6 0 1 2 2 1 1 2 8 0 1 2 193 1 1 3 2 0 1 1 3 0 1 2 4 1 1 8 11 0 1 3 1 1 1 4 1 1 1 2 12 0 1 2 4 1 1 7 9 0 1 2 2 1 1 2 12 0 1 2 7 1 1 7 10 0 1 3 2 1 1 2 12 0 1 2 6 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1495:%
149 11 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Calculation of Confidence Intervals.Rnw:ofs 1507:%
1 42 1 1 2 11 0 1 2 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1572:%
162 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Special Cases and Scenarios.Rnw:ofs 1582:%
1 20 1 1 2 4 0 1 2 4 1 1 6 8 0 1 2 4 1 1 6 8 0 1 2 18 1 1 8 16 1 1 7 9 0 1 2 2 1 1 2 8 0 1 2 2 1 1 2 8 0 1 2 4 1 1 2 8 0 1 2 22 1 1 3 5 0 1 2 27 1 1 3 5 0 1 2 39 1 1 3 5 0 1 2 23 1 1 3 5 0 1 2 19 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1879:%
173 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Analysis and Visualization.Rnw:ofs 1889:%
1 20 1 1 4 6 0 1 2 3 1 1 6 8 0 1 2 2 1 1 7 9 0 1 2 2 1 1 7 9 0 1 2 2 1 1 8 10 0 1 2 4 1 1 5 7 0 1 2 6 1 1 2 4 0 1 2 2 1 1 2 26 0 1 2 16 1 1 4 1 1 1 2 11 0 1 2 18 1 1 5 7 0 1 2 4 1 1 3 5 0 1 2 10 1 1 2 4 0 1 2 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 2120:%
184 8 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Acknowledgements.Rnw:ofs 2129:%
1 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 2134:%
194 11 1}

### 2017-09-18 rnw/Twophase_Estimators and their Application.Rnw
update Andreas 15.09.2017
update Andreas 18.09.2017(1)
update Andreas 18.09.2017(2)

@@

At this point, an inquisitive reader should notice that the calculation of $\bar{\pmb{Z}}$ and $\hat{\bar{\pmb{Z}}}$ has not been explicitly defined yet.

We

For the non-exhaustive context, assuming there is no boundary adjustment necessary, we can simply use $\hat{\bar{\pmb{Z}}}=\frac{1}{n_{1}}\sum_{x\in{s_{1}}}\pmb{Z}(x)$ and then the mathematical theory is perfectly aligned with its implementation in the \pkg{forestinventory} package.  However, in the exhaustive context under the infinite population approach, $n_1=\infty$ technically, which means that mathematically $\bar{\pmb{Z}}=\frac{1}{\lambda{(F)}}\int_{x\in{F}}\pmb{Z}(x)$. This integral is practically impossible to calculate \textit{exactly} because $\pmb{Z}(x)$ would have to be calculated for an infinite number of $x$'s in $s_1$. What we want to do to get around this is to find a way to exhaustively use all available \textbf{auxiliary information} in such a way that $n_1$ is so large that we can safely assume that $\bar{\pmb{Z}}$ is known. Practically speaking, since very large $n_1$ translates into very large input datasets which may conflict with the memory limitations in \proglang{R}, the \pkg{forestinventory} package allows the user to calculate vector $\bar{\pmb{Z}}$ on their own and input it directly into the \code{twophase()} and \code{threephase()}.

% In the \pkg{forestinventory} package, exhaustively available auxiliary information over the entire inventory area does not necessarily imply exhaustive calculation of the explanatory variables from that auxiliary information.

The key to calculating your own $\bar{\pmb{Z}}$ is to understand the difference between the explanatory variables contained in vector $\pmb{Z}(x)$ and spatial extent of the auxiliary information around the point $x$ (the so-called support) from which $\pmb{Z}(x)$ is derived. Figure \ref{fig:exh_nexh_bw} illustrates the practical difference between the exhaustive and non-exhaustive set-ups.  In order for all of the wall-to-wall auxiliary information to be exploited, the spatial arrangement of the supports should be tesselated to form a partition over the inventory area as is the case with the dark green polygons (squares tiles in this case) in Figure \ref{fig:exh_nexh_and_boundweights_a}.  As long as the size of the supports are not unreasonably large, $n_1$ is expected to be reasonably large to assume that the difference between $\hat{\bar{\pmb{Z}}}$ and $\frac{1}{n_{1}}\sum_{x\in{s_{1}}}\pmb{Z}(x)$ is neglible. This is in contrast to the non-exhaustive set-up in Figure \ref{fig:exh_nexh_and_boundweights_b} where the supports leave much of the available auxiliary information unused (represented by the light green tiles). In both cases, the vector of explanatory variables, $\pmb{Z}(x)$, can be calculated for each point $x$ using the support around that point.  It should be noted that a perfect tesselation by the supports strongly depends on the distance between the sample locations of $s_1$ as well as the support sizes and might not always be feasible in practice, in which case the assumption of tesselation must be relaxed.\par

%% NOTES:
% - first, mention what Z(x) means in practice, and how we calculate a variable stored in Z(x), i.e. use supports (maybe mention the choice of support size,
%   and that it can have an influence on model accuracy). 
% - Figure 4(b) shows how the derivation of the Z(x) in the non-exhaustive case often looks like in practice, i.e. a regular grid is given by a 
%   terrestrial inventory, densified to an s1-sample, and then supports are used to calculate the set of explanatory variables at sample location x.
%   This is in perfect aggreement with just the presented theory of the non-exhaustive estimators (except for using regular grids rather than randomly
%   placed sample points) and the forestinventory package will just use the emprirical mean of the Z(x) values given in the input dataframe, i.e. 
%   $\hat{\bar{\pmb{Z}}}=\frac{1}{n_{1}}\sum_{x\in{s_{1}}}\pmb{Z}(x)$.
% - The exhaustive case however leaves some space for the implementation:
%   This is because likewise the local density $Y(x)$ gathered in the second phase $s_2$, also the calculation of Z(x) only referrs to 
%   the sample point x, and has no spatial association (see section 2.1). Likewise the mean of the local density, the only way to determine the exact mean 
%   of $\bar{Z}$ would be to calculate the integral, i.e. in practice calculate Z(x) at an infinite number ($n_1=\infty$) of sample points $x$. In practice,
%   this is obviously impossible.
% - Figure 4(a) shows the implemented solution of an "exhaustive use" of the auxiliary information as described in Mandallaz, Breschan, Hill (2013). Is has to be noted
%   that this would perfectly enable for calculating the exact mean $\bar{Z}$ in the \textit{finite} population approach (i.e. we calculate Z(x) for the entire 
%   population of supports, and can thus calculate the exact mean $\bar{Z}$). However, this is not equal to the exact mean $\bar{Z}$ in the infinite population
%   approach for the mentioned reasons.
% - What we can do in practice is to get a reasonable approximation of $\bar{Z}$. 
%
%
%   as an approximation, i.e. if we cover the
%
%
% - mention that in the strict inf.pop.appr. frame, the supports are also allowed to overlap if this seems necessary to acquire a sufficiently large sample
%   n1 of Z(x) to get a reasonable approximation of $\bar{Z}$. This is possible because likewise the local density $Y(x)$ gathered in the second phase $s_2$,
%   also the calculation of Z(x) only referrs to the sample point, and has no spatial association.
%

>>>>

% \begin{figure}[htb]
% 	\begin{subfigure}[t]{0.5\textwidth}
% 		\centering
%     \resizebox{1.12\hsize}{!}{\includegraphics{fig/exh_and_boundweights(2).PNG}}%
% 		\caption{} \label{fig:exh_nexh_and_boundweights_a}
% 		\end{subfigure}
% 	\begin{subfigure}[t]{0.5\textwidth}
% 		\centering
%    \resizebox{0.77\hsize}{!}{\includegraphics{fig/nexh_and_boundweights.PNG}}%
% 		\caption{} \label{fig:exh_nexh_and_boundweights_b}
% 	\end{subfigure}
% \caption{Concept of exhaustive, see \textbf{(a)}, and non-exhaustive, see \textbf{(b)}, calculation of explanatory variables including boundary adjustment at the support level. Auxiliary data are in both cases available over the entire inventory area marked by the large rectangle. A set $\pmb{Z}$ of $p$ explanatory variables $x_{1},...,x_{p}$ is calculated within the small squares at each sample location $x$ (points) that falls into the forest area (green underlying polygon). w: weights used for calculating the weighted mean of each explanatory variable. Dotted circles indicate terrestrial sample plots.}
% \label{fig:exh_nexh_bw}
% \end{figure}

% At this point, an inquisitive reader should notice that the calculation of $\bar{\pmb{Z}}$ and $\hat{\bar{\pmb{Z}}}$ has not been explicitly defined yet.  
% 
% We 
% 
% For the non-exhaustive context, assuming there is no boundary adjustment necessary, we can simply use $\hat{\bar{\pmb{Z}}}=\frac{1}{n_{1}}\sum_{x\in{s_{1}}}\pmb{Z}(x)$ and then the mathematical theory is perfectly aligned with its implementation in the \pkg{forestinventory} package.  However, in the exhaustive context under the infinite population approach, $n_1=\infty$ technically, which means that mathematically $\bar{\pmb{Z}}=\frac{1}{\lambda{(F)}}\int_{x\in{F}}\pmb{Z}(x)$. This integral is practically impossible to calculate \textit{exactly} because $\pmb{Z}(x)$ would have to be calculated for an infinite number of $x$'s in $s_1$. What we want to do to get around this is to find a way to exhaustively use all available \textbf{auxiliary information} in such a way that $n_1$ is so large that we can safely assume that $\bar{\pmb{Z}}$ is known. Practically speaking, since very large $n_1$ translates into very large input datasets which may conflict with the memory limitations in \proglang{R}, the \pkg{forestinventory} package allows the user to calculate vector $\bar{\pmb{Z}}$ on their own and input it directly into the \code{twophase()} and \code{threephase()}. 
% 
% % In the \pkg{forestinventory} package, exhaustively available auxiliary information over the entire inventory area does not necessarily imply exhaustive calculation of the explanatory variables from that auxiliary information.
% 
% The key to calculating your own $\bar{\pmb{Z}}$ is to understand the difference between the explanatory variables contained in vector $\pmb{Z}(x)$ and spatial extent of the auxiliary information around the point $x$ (the so-called support) from which $\pmb{Z}(x)$ is derived. Figure \ref{fig:exh_nexh_bw} illustrates the practical difference between the exhaustive and non-exhaustive set-ups.  In order for all of the wall-to-wall auxiliary information to be exploited, the spatial arrangement of the supports should be tesselated to form a partition over the inventory area as is the case with the dark green polygons (squares tiles in this case) in Figure \ref{fig:exh_nexh_and_boundweights_a}.  As long as the size of the supports are not unreasonably large, $n_1$ is expected to be reasonably large to assume that the difference between $\hat{\bar{\pmb{Z}}}$ and $\frac{1}{n_{1}}\sum_{x\in{s_{1}}}\pmb{Z}(x)$ is neglible. This is in contrast to the non-exhaustive set-up in Figure \ref{fig:exh_nexh_and_boundweights_b} where the supports leave much of the available auxiliary information unused (represented by the light green tiles). In both cases, the vector of explanatory variables, $\pmb{Z}(x)$, can be calculated for each point $x$ using the support around that point. It should be noted that a perfect tesselation by the supports strongly depends on the distance between the sample locations of $s_1$ as well as the support sizes and might not always be feasible in practice, in which case the assumption of tesselation must be relaxed.\par

\subsubsection{Calculation of Explanatory Variables}

We will now draw our attention to the calculation of the explanatory variables from the auxiliary data for both the non-exhaustive and exhaustive case. In both cases, a set $\pmb{Z}$ of $p$ explanatory variables $x_1,...,x_p$ is calculated within a defined spatial extent (so called \textit{support}) around each sample location $x$. Figure \ref{fig:exh_nexh_and_boundweights_b} shows how the derivation of $\pmb{Z}(x)$ in the \textbf{non-exhaustive} case often looks like in practice, i.e. a regular terrestrial grid $s_2$ is given by a terrestrial inventory, densified to a larger sample $s_1$, and then supports are used to calculate the set of explanatory variables at the sample locations. This is in perfect aggreement with the just presented theory of the non-exhaustive estimator, except for using regular grids rather than randomly placed sample points. In this case, the \pkg{forestinventory} package calculates the emprirical mean of the $\pmb{Z}(x)$ values given in the input dataframe, i.e. $\hat{\bar{\pmb{Z}}}=\frac{1}{n_{1}}\sum_{x\in{s_{1}}}\pmb{Z}(x)$.\par
The \textbf{exhaustive} case however leaves some space of discussion concerning the calculation of $\pmb{Z}(x)$: This is because in the infinite population approach, the calculation $\pmb{Z}(x)$ again only referrs to the sample point $x$ and has no spatial association. Likewise the mean of the local density (i.e. the total), the only way to determine the exact mean of $\pmb{Z}(x)$ would be to calculate the integral $\bar{\pmb{Z}}=\frac{1}{\lambda(F)}\int_{x \in F} \pmb{Z}(x)$, which in practice means to calculate $\pmb{Z}(x)$ at an infinite number ($n_1=\infty$) of sample points $x$. Since this is obviously impossible, we can only try get a reasonable approximation of $\bar{\pmb{Z}}$.\par
One possibility is shown in Figure \ref{fig:exh_nexh_and_boundweights_a} which illustrates the implemented solution to the exhaustive use of the auxiliary information described in \citet{mandallaz2013b}. In order for all of the wall-to-wall auxiliary information to be exploited, the spatial arrangement of the supports were tesselated to form a perfect partition over the inventory area as is the case with the dark green polygons (squares tiles in this case). Is has to be noted that this would perfectly enable for calculating the exact mean $\bar{\pmb{Z}}$ in the \textit{finite} population approach, i.e. deriving $\pmb{Z}(x)$ for the entire finite population of supports and consequenlty calculating the exact mean $\bar{\pmb{Z}}$. While this is not equal to the exact mean $\bar{\pmb{Z}}$ in the infinite population approach, $n_1$ is still expected to be reasonably large to assume a good approximation of $\bar{\pmb{Z}}$ as long as the size of the supports are not unreasonably large. Whereas this implementation provides a convenient flexibility to switch between extimators of both the finite and infinite approach using the \textit{same} data set, it can also impose practical drawbacks. One is that a perfect tesselation by the supports strongly depends on the distance between the sample locations of $s_1$ in combination with the spatial extent of the support. Since in practice the support size will rather be chosen in order to achieve a best possible explanatory power of the regression model, thus minimizing the residual variation, a prefect tesselation might not always be feasible. In the infinite population frame however, the supports are also allowed to overlap if this seems necessary to acquire a sufficiently large sample $n_1$ of $\pmb{Z}(x)$ to get a reasonable approximation of $\bar{\pmb{Z}}$. This is again because $\pmb{Z}(x)$ only referrs to the sample point and has no spatial association. With this respect, the infinite population approach can thus provide more flexibility than the finite approach. One could even consider the use of different support sizes for an explanatory variable as long as they are consistently used at all sample locations.

Note that there are few cases where the exact mean can also be precisely calculated in the infinite population framework. The first case is when the explanatory variables are provided by polygon layers (e.g. map of development stages). In this case, one can calculate the exact mean as the area-weighted average of each categorical variable. The second case is when the exact mean can be calculated in one step, e.g. taking the mean of all height pixels of a raster canopy height model will equal the mean calculated by the use of an infinite number of supports \citep{mandallaz2013b}.

@@

%% NOTES:
% We will now quickly draw our attention to the calculation of the explanatory variables from the auxiliary data for both the non-exhaustive and exhaustive case. In both cases, a set $\pmb{Z}$ of $p$ explanatory variables $x_1,...,x_p$ is calculated within a defined spatial extent (so called \textit{support}) around each sample location $x$. Figure 4(b) shows how the derivation of Z(x) in the non-exhaustive case often looks like in practice, i.e. a regular terrestrial grid $s_2$ is given by a terrestrial inventory, densified to a larger sample $s_1$, and then supports are used to calculate the set of explanatory variables at the sample location x. This is in perfect aggreement with the just presented theory of the non-exhaustive estimators, except for using regular grids rather than randomly placed sample points, i.e. the forestinventory package will calculate the emprirical mean of the Z(x) values given in the input dataframe, i.e. $\hat{\bar{\pmb{Z}}}=\frac{1}{n_{1}}\sum_{x\in{s_{1}}}\pmb{Z}(x)$.
% The exhaustive case however leaves some space of discussion concerning the calculation of $Z(x)$:
%
%
% - first, mention what Z(x) means in practice, and how we calculate a variable stored in Z(x), i.e. use supports (maybe mention the choice of support size,
%   and that it can have an influence on model accuracy). 
% - Figure 4(b) shows how the derivation of the Z(x) in the non-exhaustive case often looks like in practice, i.e. a regular grid is given by a 
%   terrestrial inventory, densified to an s1-sample, and then supports are used to calculate the set of explanatory variables at sample location x.
%   This is in perfect aggreement with the just presented theory of the non-exhaustive estimators (except for using regular grids rather than randomly
%   placed sample points) and the forestinventory package will just use the emprirical mean of the Z(x) values given in the input dataframe, i.e. 
%   $\hat{\bar{\pmb{Z}}}=\frac{1}{n_{1}}\sum_{x\in{s_{1}}}\pmb{Z}(x)$.
% - The exhaustive case however leaves some space for the implementation:
%   This is because likewise the local density $Y(x)$ gathered in the second phase $s_2$, also the calculation of Z(x) only referrs to 
%   the sample point x, and has no spatial association (see section 2.1). Likewise the mean of the local density, the only way to determine the exact mean 
%   of $\bar{Z}$ would be to calculate the integral, i.e. in practice calculate Z(x) at an infinite number ($n_1=\infty$) of sample points $x$. In practice,
%   this is obviously impossible.
% - Figure 4(a) shows the implemented solution of an "exhaustive use" of the auxiliary information as described in Mandallaz, Breschan, Hill (2013). Is has to be noted
%   that this would perfectly enable for calculating the exact mean $\bar{Z}$ in the \textit{finite} population approach (i.e. we calculate Z(x) for the entire 
%   population of supports, and can thus calculate the exact mean $\bar{Z}$). However, this is not equal to the exact mean $\bar{Z}$ in the infinite population
%   approach for the mentioned reasons.
% - What we can do in practice is to get a reasonable approximation of $\bar{Z}$. 
%
%
% - mention that in the strict inf.pop.appr. frame, the supports are also allowed to overlap if this seems necessary to acquire a sufficiently large sample
%   n1 of Z(x) to get a reasonable approximation of $\bar{Z}$. This is possible because likewise the local density $Y(x)$ gathered in the second phase $s_2$,
%   also the calculation of Z(x) only referrs to the sample point, and has no spatial association.
%
% - mention that the support size thereby does not have to match the plotsize of the terrestrial inventory. In the strict inf.pop.appr. frame, the supports are also allowed to overlap if this seems necessary to acquire a sufficiently large sample n1 of Z(x) to get a reasonable approximation of $\bar{Z}$. This is possible because likewise the local density $Y(x)$ gathered in the second phase $s_2$, also the calculation of Z(x) only referrs to the sample point, and has no spatial association. In fact, the support size will in practice be chosen in order to achieve a best possible explanatory power of the regression model, thus minimzing the residual variation. mention that a change of support size between sample points for a given expl. variable is not allowed (because.... Daniel ?)
%
%
